TODO

### 2021-03-11 publications/The_tool_intro/paper.tex
pub: added 2 architecture figures

	\section{Analysis framework}
	\subsection{Representation - Architecture} % 4 hasáb - Dániel
	% belső gráf, a koncepció
	% elemzések
	% app megvalósítás

	\subsection{Experts} % 1 hasáb - Dániel
	% kisebb gráf ábra
	\subsection{Testing} % 1 hasáb - Gabi
	% külön modul
	% elvi részei jelenlenek meg
	% ilyen olyan teszt, messziről melyik hogy

>>>>

	\section{Analysis framework}

	\subsection{Representation - Architecture} % 4 hasáb - Dániel
	% belső gráf, a koncepció
	% elemzések
	% app megvalósítás

  \begin{figure}
    \includegraphics[width=0.18\textwidth]{figures/arch-top.pdf}
    \caption{TODO}\label{fig:arch-top}
  \end{figure}

  \begin{itemize}
    \item Figure \ref{fig:arch-top} 
    \item User extracts information (including metrics, object codes, verified properties) from the code using applications (corresp. backends). Applications provide services by utilizing the code knowledge stored in the knowledge graph by the analysers of the infrastructure layer (corresp. frontend). The collaboration of the application and the analysers is orchestrated by a controller module.
  \end{itemize}

	\subsection{Experts} % 1 hasáb - Dániel
	% kisebb gráf ábra

  \begin{figure}
    \includegraphics[width=0.3\textwidth]{figures/arch-deps.pdf}
    \caption{TODO}\label{fig:arch-deps}
  \end{figure}

  \begin{itemize}
    \item Figure \ref{fig:arch-deps} 
    \item More granular.
    \item Analysers depend on each other. Applications only depend on one or more analysers.
    \item Controller manages dependencies.
  \end{itemize}

	\subsection{Testing} % 1 hasáb - Gabi
	% külön modul
	% elvi részei jelenlenek meg
	% ilyen olyan teszt, messziről melyik hogy
